Assessing Tor's Usability as a Censorship Circumvention Tool

### 2015-05-12 cs261n-paper/paper.tex
ux methodology

@@

\subsection{Assumptions} 
{\color{red} do I need this here?}

@@

\begin{figure}[t]
\includegraphics[width=\linewidth]{configuration-dialog.png}
\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
configure their network settings to circumvent censorship. The instructions asks users to 
choose a pluggable transport or enter custom bridges.}
\label{dialog}
\end{figure}

@@

Tasks 1--3 test how easy it was for a user to search for, download, and install Tor Browser 
correctly for use and if they understood that they had done the tasks correctly. 
Since no software is useful if the user is not able to access it, we found it valuable
to test the usability of this process.  Additionally, tasks 4--6 highlight Tor's ``irregular'' behavior 
comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.

>>>>

While our pilot was insightful, the experiment itself is not very reproducible, as it requires
a specific target audience (journalists who have recently reported in other countries) along 
with specific guidance and feedback on how to perform a cognitive walkthrough. This makes it hard
for the research community to prove or build on any findings. Therefore, we take precautions
to ensure that our full-scale study will be reproducible.

@@

@@

\begin{figure}[t]
\includegraphics[width=0.5\textwidth]{configuration-dialog.png}
\caption{The fourth and final window of the Tor configuration dialog is what users will use to 
configure their network settings to circumvent censorship. The instructions asks users to 
choose a pluggable transport or enter custom bridges.}
\label{dialog}
\end{figure}

@@

Tasks 1-3 test how easy it was for a user to search for, download, and install Tor Browser 
correctly for use and if they understood that they had done the tasks correctly. 
Since no software is useful if the user is not able to access it, we found it valuable
to test the usability of this process.  Additionally, tasks 4-6 highlights Tor's ``irregular'' behavior 
comparatively to other web browsers. Specifically, gauge user reactions to Tor's default
privacy-preserving search engine Startpage,  longer loading times and performance for videos, 
and disappearing tabs upon starting a new identity. Lastly, we asked our users to 
interact with and describe buttons on the toolbar to gauge user comprehension of how Tor functioned.
